The Evolution of Neighbourhood Crime in Toronto (2019–2024)

### 2025-05-31 paper/paper.qmd
Update paper.qmd

We utilize the programming language Python [@python] alongside Polars [@polars] and scikit-learn [@scikit-learn] for the paper’s data cleaning and analysis.^[The workflow and GitHub-based project structure follow best practices from @tellingstories.]

>>>>

We utilize the programming language Python [@python] alongside Polars [@polars] and scikit-learn [@scikit-learn] for the paper’s data cleaning and analysis.
